---
title: "Bootstrap and Confidence Interval"
author: "Debit Paudel"
date: "12/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Bootstrap is a resampling method where large numbers of samples of the same size are repeatedly drawn,**with replacement**, from a single original sample.
Resample, calculate a statistic (e.g. the mean), repeat this hundreds or thousands of times and you are able to estimate a precise/accurate uncertainty of the mean (confidence interval) of the data’s distribution.

```{r}
x <- runif(10)
hist(x)
mean(x)
resample <- sample(x, replace = TRUE)
mean(resample)
library(dplyr)
library(ggplot2)
# Resample 100 times, and find the mean of each
tibble(num = 1:100) %>% 
    group_by(num) %>% 
    mutate(means = mean(sample(x, replace = TRUE))) %>% 
    ggplot(aes(x = means)) +
    geom_freqpoly()
    
# Resample a 5000 times, and find the mean of each
tibble(num = 1:5000) %>% 
    group_by(num) %>% 
    mutate(means = mean(sample(x, replace = TRUE))) %>% 
    ggplot(aes(x = means)) +
    geom_freqpoly()

```
There is an R package that does bootstraping called `boot`. `boot` function we need a function that calculates the average based on the resampling of the data. that Takes two arguments, a value (`x`) and a value resampling vector (`I`).

```{r}
library(boot)
# Create a function to take a resample of the values, 
# and then calculate the mean
boot_mean <- function(original_vector, resample_vector) {
    mean(original_vector[resample_vector])
}
# R is number of replications
mean_results <- boot(x, boot_mean, R = 2000)
# Load broom to get a tidy dataframe as output.
library(broom)
tidy(mean_results)
# Calculate the confidence intervals
boot.ci(mean_results)


# If you bootstrap for a statistic with two values, the individual rows are
# resampled. However, the rows are still paired together (no reshuffling of the
# order occurs).


boot_corr <- function(data, resample_vector) {
    cor(data$x[resample_vector], data$y[resample_vector])
}
ds <- data.frame(y = runif(10), x = runif(10))
# Original correlation
cor(ds$x, ds$y)
# Bootstrapped correlation
cor_results <- boot(ds, boot_corr, R = 100)
tidy(cor_results)
# Plus confidence interval
boot.ci(cor_results)

boot_corr <- function(data, resample_vector) {
    cor(data$x[resample_vector], data$y[resample_vector])
}
ds <- data.frame(y = runif(10), x = runif(10))
# Original correlation
cor(ds$x, ds$y)
# Bootstrapped correlation
cor_results <- boot(ds, boot_corr, R = 100)
tidy(cor_results)
# Plus confidence interval
boot.ci(cor_results)
```
Hence, we are able to compute the confidence intervals too.


